simple summary of objective function for rank 1 vs rank 0

### 2017-06-21 analysis/Obj_summary.Rmd
Files commited by wflow_commit.

In this case, we check the objective funciton with penalty term, and it does monotonically increase.

>>>>

In this case, we check the objective funciton with penalty term, and it does monotonically increase. [rank 0 vs rank 1: fdr with penalty](Objcheck_2.html)

**now we have two methods (fdr, shrink), and both of them have monotonically increasing corresponding objective function in each case.**

> i) fit flash (with or without penalty)
>
> ii) check if flash-obtained objective function exceeds the K=0 objective. (note: not the limit of the objective as g_f, g_l -> 0, but the actual objective at g_f=g_l=0). If not, set result to g_f=g_l = 0. If so, keep g_f, g_l as output by flash.
>
> -- Matthew's advice.

- we  have done the (i), and we found that it is reasonable to do the (ii). This is because we find that $diff(LB(fitted) - LB(rank=0))$ is negatively correlated with RMSE, which means larger obj value goes with smaller RMSE. So it makes sense we cut the obj value off at the rank 0 model.
- (ii) is easy to implement.

#### questions

1. how to deal with $(\lambda_0 - 1) log \pi_0$ when $\pi_0 = 0$?
2. now we only have two cases: shrink with $\lambda_0 = 1$ and fdr with $\lambda_0 = 10$. Do we need more choice of $\lambda_0$?
